Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-17 manuscript/response_to_reviews.Rmd

L137-140: mixing cores from dying and surviving individuals could be problematic. Did you find any association between survival and previous drought resistance? Was mortality different across species?

L160: you mean a log-log regression, right?

L181: N=3 individuals per species is really quite low. In addition, by sampling up to 8 m height you would probably be sampling less exposed branches from taller trees, which could confound your results.

*from Lawren: "Re the trait values, I believe we would see species differences, even with n=3, looking at the means and SD presented. Suggest to run an ANOVA on each trait (and/or a MANOVA on all traits) and put the significance values in a new row in Table 3.  (BTW also suggest limiting values in Table 3 to 3 sig figs, and presenting SE in that Table with the means rather than SD)."*

### 2020-07-17 manuscript/tables&figures.Rmd
added two Fig.4 options to figures

![**Figure 4. Visualization of best models for all droughts combined and for each drought separately.** Model coefficients are given in Table S6. **THIS IS NOT YET CORRECT (having trouble making gg-plot work. THE POSITIVE HEIGHT EFFECT FOR 1999 IS WRONG. FINAL FIG WILL MATCH MODELS IN TABLE S6.** ](tables_figures/publication/regr_visuals.png){width=500px}

>>>>

![**Figure 4_option1. Visualization of best model for all droughts combined.** Model coefficients are given in Table S6.** ](tables_figures/publication/best_model_with_data.png){width=500px}

![**Figure 4_option 2. Visualization of best model for all droughts combined and for each drought separately.** Model coefficients are given in Table S6. **confidence intervals would be added.** ](tables_figures/publication/best_models_ind_years.png){width=500px}
